An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
Modification details

	\noindent\textbf{\underline{Puck \cite{puck}.}}  
	While simultaneous filtering performs well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints. In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.

@@

	\textit{\textbf{Peak memory usage.}}
	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage. This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. On large-scale datasets, CPAS exhibits slightly lower memory usage compared to other algorithms. Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.

@@

	\subsection{Range Filtering}
	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range filtering algorithms.
	\subsubsection{Time and Space overhead of index construction.}
	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}

@@

		% 三图横排
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_ndex_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

>>>>

	\noindent\textbf{\underline{Puck \cite{puck}.}}  
	While simultaneous filtering algorithms perform well in most scenarios, it may underperform when only a small portion of data satisfies attribute constraints. In such cases, a pre-filtering strategy—applying attribute constraints prior to ANN search—can be more effective.

@@

	\textit{\textbf{Peak memory usage.}}
	As shown in Figure~\ref{fig:memory_mb_comparison_query1}, on small-scale datasets, all methods except NHQ exhibit low memory usage. This is because NHQ adopts the kgraph approach for index construction, which requires loading the entire graph data into memory and maintaining a complete graph structure, leading to relatively high memory overhead. On large-scale datasets, CAPS exhibits slightly lower memory usage compared to other algorithms. Due to their special characteristics, databases are not included in the peak memory usage testing during index construction.

@@

	\subsection{Range Filtering}

	\subsubsection{Time and Space overhead of index construction.}
	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}

@@

		% 三图横排
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}
